Data Preparation

### 2019-01-10 Data Preparation.Rmd
empty space
code for removing stop words

To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
```{r tidy d_description}
d_overview <- d_description %>%
  select(Code, `Calendar Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)
print(d_overview_tidy)

@@

### Stemming
We then use the function `hunspell__stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`. We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell__stem`). We then apply `stem_hunspell` on the words of `d_overview_tidy`. Since, `stem_hunspell` is not a vectorized function and the number of words in `d_overview_tidy` is large, we first use distinct on the `word` variable to find a list containing *once* each term present in the course overviews. Then, we apply the function `stem_hunspell` on this list. We save the terms and their stems in the tibble `stems`. Since the course descriptions can be conceptualized as a subset of the course overviews, the tibble `stems` contains all the terms present in the descriptions and can therefore safely used to stem the words in `d_description_tidy`.
```{r stemming dictionary, cache = TRUE}
stem_hunspell <- function(term) {
  stems   <- hunspell_stem(term)[[1]] # look up the term in the dictionary
  n_stems <- length(stems)            # number of stems
  if (n_stems == 0) term              # if no stems, return original term
  else              stems[[n_stems]]  # if multiple stems, return last (most basic) stem
}

dictionary <- select(d_overview, Code, word) %>%
  rbind(d_manual) %>% 
  select(word) %>%
  distinct %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))

# terms for which the stem differs from the original word
filter(dictionary, word != word_stem)

my_sw <- c("______________________________________________________________________________")

data("stop_words")  #imports common stopwords

my_stop_words <- data.frame (word = c(1:11, "students", )) #no stemming ("students")

manuals_tokens_preprocessed <- manuals_tokens %>%
  anti_join(stop_words)     %>%
  anti_join(my_stop_words) %>%
  anti_join(number_stopwords, by = c("word"="word"))

```{r stemming d_description}
d_overview <- d_overview %>%
  left_join(dictionary, by = "word") %>%
  rename(word_original = word,
         word = word_stem) %>%
  filter(!word %in% stop_words$word)

d_description <- d_description %>%
  left_join(dictionary, by = "word") %>%
  rename(word_original = word,
         word = word_stem) %>%
  filter(!word %in% stop_words$word)

rm(stems, stem_hunspell)
print(d_overview_stem) # See humanities - humanity
```
### Removing Stopwords

>>>>

We first create two tibbles `d_overview_tidy` and `d_description_tidy` that respectively store the overviews and the descriptions in the tidy text format, with one row per course-year-word.
```{r tidy d_description}
d_overview <- d_description %>%
  select(Code, `Calendar Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)
print(d_overview_tidy)

@@

### Stemming
We then use the function `hunspell__stem`, which returns valid stems for a given word, to stem the words in the tibbles `d_overview_tidy` and `d_description_tidy`. We first create a function `stem_hunspell` which, given a term, returns its most basic stem (the last one from the list of stem returned by `hunspell__stem`). We then apply `stem_hunspell` on the words of `d_overview_tidy`. Since, `stem_hunspell` is not a vectorized function and the number of words in `d_overview_tidy` is large, we first use distinct on the `word` variable to find a list containing *once* each term present in the course overviews. Then, we apply the function `stem_hunspell` on this list. We save the terms and their stems in the tibble `stems`. Since the course descriptions can be conceptualized as a subset of the course overviews, the tibble `stems` contains all the terms present in the descriptions and can therefore safely used to stem the words in `d_description_tidy`.
```{r creating dictionary, cache = TRUE}
stem_hunspell <- function(term) {
  stems   <- hunspell_stem(term)[[1]] # look up the term in the dictionary
  n_stems <- length(stems)            # number of stems
  if (n_stems == 0) term              # if no stems, return original term
  else              stems[[n_stems]]  # if multiple stems, return last (most basic) stem
}

my_dictionary <- rbind(select(d_overview, word),
                       select(d_manual  , word)) %>%
  distinct %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))

# terms for which the stem differs from the original word
filter(my_dictionary, word != word_stem)
```

```{r stemming}
stem_with_dictionary <- function(data)  data %>%
  left_join(my_dictionary, by = "word") %>%
  rename(word_original = word,
         word = word_stem)

d_overview    <- stem_with_dictionary(d_overview)
d_description <- stem_with_dictionary(d_description)
d_manual      <- stem_with_dictionary(d_manual)

rm(stem_hunspell, my_dictionary, stem_with_dictionary)
print(d_overview) # See humanities - humanity
```

### Removing Stopwords

```{r}
# own stopwords
sw_own <- c("______________________________________________________________________________")

remove_sw <- function(data) data %>%
  filter(! word %in% c(stop_words$word,
                       sw_own))

d_overview    <- remove_sw(d_overview)
d_description <- remove_sw(d_description)
d_manual      <- remove_sw(d_manual)

rm(stem_hunspell, my_dictionary, remove_sw, sw_own)
```
